Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-16 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: updated corner plot

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/tmp_corner_plot.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $M_f$, and redshift $z$ for GW150915, using the same waveform model,
but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
dCS gravity and $j=0$). The contours represent 90\% credible regions.
%
We see that the introduction of the non-GR parameters does not bias the inference on the source parameters.
%
\hs{TODO: increase font size and move it to an Appendix.}
}
\label{fig:corner_plot}
\end{figure}

>>>>

\begin{figure}[t]
\includegraphics[width=0.9\columnwidth]{figs/tmp_GW150914_intrinsic_params_remnant.pdf}
\caption{(Color online).~Corner plot showing that the inferred final spin $\chi_f$,
detector-frame remnant mass $(1 + z) \, M_f$ for GW150915, using the same waveform model,
but without (blue contours) and with the non-GR parameters different from zero (orange contours, for
dCS gravity and $j=0$). The contours represent 90\% credible regions.
%
We see that the introduction of the non-GR parameters does not bias the inference on the source parameters.
}
\label{fig:corner_plot}
\end{figure}
